---
title       : Australian Airport Passenger-traffic Analysis (AAA)
subtitle    : Interactive analysis of AAA
author      : just_np
job         : BI Consultant
framework   : io2012          # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js    # {highlight.js, prettify, highlight}
hitheme     : solarized_light # tomorrow 
widgets     : [polycharts, bootstrap, shiny, interactive]
mode        : selfcontained   # {standalone, selfcontained,draft}
ext_widgets : {rCharts: [libraries/nvd3]}
knit        : slidify::knit2slides
---

### Australian Airport Passenger-traffic Analysis (AAA)

Australian Airport Passenger-traffic Analysis (AAA) app provides a interactive analysis of domestic and international passenger movements across all states and cities of Australia.

The raw data for this analysis is downloaded from Bureau of Infrastructure, Transport and Regional Economics (BITRE) http://www.bitre.gov.au

The data used in AAA is spanned from year 1985 to 2013

In the following slides show analyse the Australian Airport Traffic dataset

---


```{r, echo = FALSE, cache = TRUE}
# Read airtraffic data
auAirTrafficRaw <- read.csv("auAirTraffic_V2.csv")

# Remove the records without blank Ranks
auAirTraffic <- subset(auAirTrafficRaw, RANK != '-')

suppressMessages(library(rCharts))
suppressMessages(library(slidify))
```

## Interactive Internationa Airport Passenger Movements Analysis's by Airport type

```{r echo = F, results = 'asis'}
stkPlot <- nPlot(AIRTRAFFIC_TOTAL ~ YEAR, group = 'STATECODE', 
                 data = subset(auAirTraffic, TRAFFICTYPE == 'International'& AIRTRAFFIC_TOTAL > 0), 
                 type = 'multiBarChart', dom = 'stkchart', width = 600)                   
        stkPlot$yAxis(tickFormat = "#! function(d) {return '' + d3.format(',.')(d)} !#")
        stkPlot$chart(margin = list(left = 100))
        stkPlot$yAxis( axisLabel = "International passenger - Movements (millions)", width = 80)
stkPlot$print('stkchart')
```

---

## Interactive Domestic Airport Passengers Movements Analysis's for state Northern Territory (NT)

```{r echo = F, results = 'asis'}
auAirports <- subset(auAirTraffic, TRAFFICTYPE == 'Domestic' & STATECODE == 'NT', AIRTRAFFIC_TOTAL > 0,)
sccplot <- nPlot(AIRTRAFFIC_TOTAL ~ YEAR, group = 'AIRPORT', data = auAirports, 
                         type='scatterChart', dom = 'sctChart', width = 600)
sccplot$yAxis(axisLabel = "NT - Domestic Passenger Movements (millions)", tickFormat = "#! function(d) {return '' + d} !#")
sccplot$xAxis( axisLabel = "Year")
sccplot$chart(size = '#! function(d){return d.AIRTRAFFIC_TOTAL} !#')
sccplot$yAxis(tickFormat = "#! function(d) {return '' + d3.format(',.')(d)} !#")
sccplot$chart(margin = list(right = 100))
sccplot$print('sctChart')
```

---

## Interactive Domestic Passengers Movements Analysis's by year

```{r echo = F, results = 'asis'}
auAirports <- subset(auAirTraffic, TRAFFICTYPE == 'Domestic' & AIRTRAFFIC_TOTAL > 0,)
sccplot1 <- nPlot(AIRTRAFFIC_TOTAL ~ YEAR, group = 'STATECODE', data = auAirports, 
                  type='scatterChart', dom = 'sctchart1', width = 600)
sccplot1$yAxis(axisLabel = "Domestic Passengers Movements (millions)", tickFormat = "#! function(d) {return '' + d} !#")
sccplot1$xAxis( axisLabel = "Year")
sccplot1$chart(size = '#! function(d){return d.AIRTRAFFIC_TOTAL} !#')
sccplot1$yAxis(tickFormat = "#! function(d) {return '' + d3.format(',.')(d)} !#")
sccplot1$chart(margin = list(right = 100))
sccplot1$print('sctchart1')
```

---

## Interactive Domestic and International Passengers Movements (millions) Analysis's by year

```{r echo = F, results = 'asis'}
auAirports <- subset(auAirTraffic, AIRTRAFFIC_TOTAL > 0,)
sccplot2 <- nPlot(AIRTRAFFIC_TOTAL ~ YEAR, group = 'TRAFFICTYPE', data = auAirports, 
                  type='scatterChart', dom = 'sctchart2', width = 600)
#sccplot2$yAxis(axisLabel = "Movements (millions)")
sccplot2$yAxis(tickFormat = "#! function(d) {return '' + d} !#")
sccplot2$xAxis( axisLabel = "Year")
sccplot2$chart(size = '#! function(d){return d.AIRTRAFFIC_TOTAL} !#')
sccplot2$yAxis(tickFormat = "#! function(d) {return '' + d3.format(',.')(d)} !#")
sccplot2$chart(margin = list(right = 100))
sccplot2$chart(color = c('red', 'blue'))
sccplot2$print('sctchart2')
```
